\documentclass[12pt]{article}
%宏包
\usepackage{amsmath}%数学符号
\usepackage{amssymb}%数学符号
\usepackage{amsthm}%数学符号
\usepackage{geometry}%界面布局
\usepackage{natbib}%bibtex
\usepackage{tikz}%交换图
\usepackage{tikz-cd}%交换图
\usepackage{quiver}%交换图
\usepackage{float}%浮动体固定
\usepackage{caption}%图片标题
\usepackage[colorlinks,linkcolor=blue]{hyperref}%超链接
\usepackage{enumerate}%计数列表
\usepackage{tabularx}%控制列宽
\usepackage{CTEX}
\usepackage{caption}%字体
\ctexset{today=old}
   
%页面设置
\linespread{1.2}
\geometry{a4paper,left=2cm,right=2cm,top=2.5cm,bottom=2cm}
%\geometry{a4paper,left=2cm,right=2cm,top=2.5cm,bottom=2cm}
%环境和宏指令
\newenvironment{prooff}{{\noindent\it\textcolor{cyan!40!black}{Proof}:}\,}{\par \vskip 1cm}
\newenvironment{proofff}{{\noindent\it\textcolor{cyan!40!black}{Proof of the lemma}:}\,}{\qed \par}
\newcommand{\bbrace}[1]{\left\{ #1 \right\} }
\newcommand{\bb}[1]{\mathbb{#1}}
\newcommand{\p}{^{\prime}}
\renewcommand{\mod}[1]{(\text{mod}\,#1)}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\spec}[1]{\text{Spec}({#1})}
\newcommand{\rarr}[1]{\xrightarrow{#1}}
\newcommand{\larr}[1]{\xleftarrow{#1}}
\newcommand{\emptyy}{\underline{\quad}}
\newenvironment{enu}{\begin{enumerate}[(1)]}{\end{enumerate}}
%ctrl+点击文本返回代码  选中代码 ctrl+alt+j 为代码查找文本

%定理环境
\theoremstyle{definition}
\newtheorem{defn}{Definition}[section]
\newtheorem{coro}[defn]{Corollary}
\newtheorem{theo}[defn]{Theorem}
\newtheorem{exer}[defn]{Exercise}
\newtheorem{rema}[defn]{Remark}
\newtheorem{lem}[defn]{Lemma}
\newtheorem{prop}[defn]{Proposition}
\newtheorem{nota}[defn]{Notation}
\newtheorem{exam}[defn]{Example}
\title{Courses Description(revised version)}
\author{Erzhuo Wang}
\date{}
\begin{document}
\maketitle 

Functions of Real Variable(Real Analysis):
\begin{enu}
    \item Textbook: Folland's Real Analysis
    \item Content: Measure space, Lebesgue Measure, Integration, 
    Lebesgue-Radon-Nikodym Theorem, $L^p$ Space, Radon Measure 
    and Risez Representation Theorem for LCH Space.
\end{enu}

Theory of One Complex Variable: 
\begin{enu}
    \item Textbook: Stein's Complex Analysis
    \item Content: Holomorphic and Meromorphic functions, Residue Forumula, 
    Classification of Singularity, Entire Functions, 
    Elliptic Functions. 
\end{enu}

Functional Analysis: 
\begin{enu}
    \item Textbook: Functional Analysis written by Gongqing Zhang(张恭庆) 
    \item Content: Banach space, 
    Open Mapping Theorem, Closed Graph Theorem, Hilbert Space,  
    Spectral Theory of Operators, Fredholm Operators.
\end{enu}
Abstract Algebra: 
\begin{enu}
    \item Textbook: Abstract Algebra written by Weisheng Qiu(丘维声)
    \item Content: Group, Subgroup group, Quotient Group, Group Action, Sylow Theorem, 
    Ring, PID and UFD, Field, Algebraic Extension, Finite Field, 
    Cyclotomic Field, Galois Theory, Computation of Galois Group. 

\end{enu}



Algebra Seminar: 
\begin{enu}
    \item Textbook: A Course in Commutative Algebra(GTM 256)
    \item Content: Zariski topology, 
    Specturm of Commutative Ring, Krull Dimension, Localization, 
    Integral Extension, Chain Condition, Hilbert Basis Theorem, Princial Ideal Theorem.   
\end{enu}

Analytic Number Theory: 
\begin{enu}
    \item Textbook: Lecture notes written by Professor Ping Xi. 
    \item Content: Abel Summation, Euler-Maclaurin, Poisson Summation, 
    Arithmetic Function, Mean Value of Arithmetic Function, Prime Number Theory, 
    Perron Formula, Dirchlet Series, Exponential Sum, Bombieri-Vinogradov Theorem. 
\end{enu}

Differential Manifold: 
\begin{enu}
    \item Textbook: Loring Tu's Smooth Manifold 
    \item Content: Smooth Manifold and Smooth Maps, Tagent Space, 
    Immersion and Submersion, Submanifold, Vector Field, Differential Form, Integration on Manifold. 
\end{enu}

Topology: 
\begin{enu}
    \item Textbook: Topology written by Chengye You(尤承业)
    \item Content: Point Set Topology, Fundemental Group, Covering Space, Classification of Closed Surfaces.
\end{enu}


\blue{The following three courses were taken in a summer school holded by Chinese
Academy of Sciences rather than Xi'an Jiaotong University, so they don't appear on my transcript.} 
\vskip 1cm 

Algebraic Geometry: 
\begin{enu}
    \item Textbook: Lecture notes written by Professor Shizhang Li(李时璋)
    \item Content: Sheaf Theory, Affine Scheme, 
    Basic Propositions of Scheme and morphism of Scheme, 
    open immersion and closed immersion, fiber product, Quasi-coherent modules
\end{enu}

Algebraic Number Theory: 
\begin{enu}
    \item Textbook: Lecture notes written by Professor Jingren Chi(迟敬人) 
    \item Content: Minkowski Theory, Ramification Theory, Density Theorem, 
    Class Field Theory, Artin L-functions.
\end{enu}

Representation Theory: 
\begin{enu}
    \item Textbook: Lecture notes and Serre's Linear Representations of Fintie Groups
    \item Content: Group Algebra, Basic Examples of Linear Representation, Character Theory, 
    , Induced Representation.
\end{enu}
\end{document}