\documentclass[12pt]{article}
%宏包
\usepackage{amsmath}%数学符号
\usepackage{amssymb}%数学符号
\usepackage{amsthm}%数学符号
\usepackage{geometry}%界面布局
\usepackage{natbib}%bibtex
\usepackage{tikz}%交换图
\usepackage{tikz-cd}%交换图
\usepackage{quiver}%交换图
\usepackage{float}%浮动体固定
\usepackage{caption}%图片标题
\usepackage[colorlinks,linkcolor=blue]{hyperref}%超链接
\usepackage{enumerate}%计数列表
\usepackage{tabularx}%控制列宽
\usepackage{CTEX}
\usepackage{caption}%字体
\ctexset{today=old}
   
%页面设置
\linespread{1.2}
\geometry{a4paper,left=2cm,right=2cm,top=2.5cm,bottom=2cm}
%\geometry{a4paper,left=2cm,right=2cm,top=2.5cm,bottom=2cm}
%环境和宏指令
\newenvironment{prooff}{{\noindent\it\textcolor{cyan!40!black}{Proof}:}\,}{\par \vskip 1cm}
\newenvironment{proofff}{{\noindent\it\textcolor{cyan!40!black}{Proof of the lemma}:}\,}{\qed \par}
\newcommand{\bbrace}[1]{\left\{ #1 \right\} }
\newcommand{\bb}[1]{\mathbb{#1}}
\newcommand{\p}{^{\prime}}
\renewcommand{\mod}[1]{(\text{mod}\,#1)}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\spec}[1]{\text{Spec}({#1})}
\newcommand{\rarr}[1]{\xrightarrow{#1}}
\newcommand{\larr}[1]{\xleftarrow{#1}}
\newcommand{\emptyy}{\underline{\quad}}
\newenvironment{enu}{\begin{enumerate}[(1)]}{\end{enumerate}}
%ctrl+点击文本返回代码  选中代码 ctrl+alt+j 为代码查找文本

%定理环境
\theoremstyle{definition}
\newtheorem{defn}{Definition}[section]
\newtheorem{coro}[defn]{Corollary}
\newtheorem{theo}[defn]{Theorem}
\newtheorem{exer}[defn]{Exercise}
\newtheorem{rema}[defn]{Remark}
\newtheorem{lem}[defn]{Lemma}
\newtheorem{prop}[defn]{Proposition}
\newtheorem{nota}[defn]{Notation}
\newtheorem{exam}[defn]{Example}
\title{Personal Statement}
\author{Erzhuo Wang(王尔卓)}
\date{}
\begin{document}
\maketitle 
\section{Basic Information}
I am a senior student at Xi'an Jiaotong University majoring in Mathematics. 
My research interest is number theory, especially Modular Forms, Automorphic Forms and their L-functions. 
I am seeking to pursue a doctoral degree at University at Buffalo.
\section{Experiences}
I discovered my passion for Number Theory in high school because of a magic theorem says an odd prime number 
$p \equiv 1\mod{4}$ if and only if it can be written as the sum of two perfect squares. 
After entering campus, I began to learn number theory in a structured way.

During my bachelor's degree,
I read the initial two chapters and final chapter (Algebraic number field, local field and L-functions) of Neukirch's Algebraic Number Theory, 
the first three chapters of Fred Diamond's A First Course in Modular Form (basic concepts in Modular Form, dimension formula)
and Tate's thesis (analytic continuation of Hecke L-functions).  

In my first year on campus, I focused on studying foundational subjects in Mathematics such as Linear Algebra and Analysis.
I attended a seminar Professor Xi organized that year. 
We discussed the first few chapters of GTM 84, covering propositions of Gauss Sum and some results about the number of 
solutions of some special
Diophantus equations over finite field. 

During the second year summer vacation, 
I successfully completed the written test and interview to participate in a summer school held by the Chinese Academy of Sciences. 
At the school, I learned basic concepts in Algebraic Geometry, Algebraic Number Theory, and Representation Theory. 

In the third year, I enrolled in the Analytic Number Theory course taught by Professor Xi. 
I learned about classical ideas about exponential sums, Sieve method and the Prime Number Theorem. 
After that, I began reading Tate's thesis and obtained a comprehensive understanding of Hecke L-functions. 
\section{Future Picture}
In my future study and research, what I really want to do is to 
discover the deep connection between number theory and other areas in mathematics such as Representation Theory 
and Dynamic System. 
For example, I really appreciate Professor Venkatesh and Nelson's work since they apply many different 
methods from Lie Group, Microlocal Analysis and Dynamic System to study subconvex bound problem. 
But I cannot understand them completely at the moment. 

Furthermore, I truly want to know how special values of different 
L-functions reflect the information of different arithmetic objects. 
The reason is that 
I find the Analytic Class Formula
$$
\lim_{s\rightarrow 1}(s-1)\zeta_K(s)=\operatorname{Vol}\left(\bb{I}_K^1/K^\times\right)=\frac{2^{r_1}(2\pi)^{r_2}h_K R_K}{\omega_K \sqrt{|d_K|}}
$$
has many useful and powerful corollaries. I want to learn and discover more results like that.

% \section{Why UNT?}
% After looking at the faculty members at UNT, I think UNT is incredibly 
% suitable for me because the research areas in number theory at UNT are various, including  
% arithmetic geometry, elliptic curve/iwasawa theory, and modular forms/automorphic forms. 
% Meanwhile, I'm interested in the connection of various topics in number theory .
% \section{Something About My Transcript}
% There's a non-accurate translation in my transcript.
% “Functions of Real Variable” from its Chinese name “实变函数” should be 
% “Real Analysis” since in this course, we mainly study basic 
% propositions of measure space, measurable functions, Lebesgue measure and Radon measure.

% In the course called “Algebra Seminar”, we mainly discuss the first few chapters of 
% GTM 256(A Course in Commutative Algebra).

% I took several programming and algorithm courses because I was interested in computer science, but now I am more interested in doing research in pure mathematics.
\end{document}